---
title: "Social Network Analysis <br/> Home Assignment 3"
author: "Ramil Mirzaaghayev"
date: "due date - 03.06.2019 23:59"
output:
  word_document:
    toc: yes
  pdf_document:
    toc: yes
  html_document:
    toc: yes
---
# Network communities
Please send your reports to hse.ntwks@gmail.com with the subject of of the following structure:<br/>
*[MAGOLEGO SNA 2017] {LastName} {First Name} HW{Number}*

Late submission policy: -1 point per day

Use this file as a template for your report.\
Support your computations with figures and comments. Send ONLY .Rmd versions of your report.

```{r, echo=FALSE}
library(igraph)
```


## Yahoo Music Network

For this assignment, you have to load [the part of Yahoo Music Network](https://drive.google.com/file/d/0Bwd5a7NScgMtNElfOFdSbE1UYnM/view). Archive contains network in GML format and corresponding list of artists.

```{r}
## Put your code here
z = read.graph("music2K.gml", format = "gml")
```

Edges in this network appear if enough number of users have given ratings to both music bands. Note, that edges are weighted with similarity of the ratings.


### 1. Preprocessing

This network needs to be preprocessed. Do the steps, described on seminar, to make it look properly. How many vertices and edges were deleted?

```{r Preprocess the graph, echo=TRUE}
## Put your code here

# Preprocess the graph
g = delete.vertices(z, degree(z) == 0)
simplify(g)
#plot(g)

# Check the result of preprocessing
deltaV = length(V(z))-length(V(g))
deltaE = length(E(z))-length(E(g))

paste("After preprocessing the size of vertices decreased by",deltaV)
paste("After preprocessing the size of edges decreased by",deltaE)
```

### 2. Clustering

Define clusters for this networks using one of the algorithms described on lectures and seminars:
```{r}
## Put your code here
mm <- fastgreedy.community(g)
plot(rev(mm$modularity), xlab = 'Number of clusters', ylab = 'Modularity value')
#plot(mm, g)
```
```{r}
typeof(mm)
```

Compute density of obtained clusters:
```{r, echo=TRUE}
## Put your code here
#groups(mm)
# 
density.list = list()
for (i in seq(length(groups(mm)))){
    sg = induced_subgraph(g, mm$membership==i)
    density.sg = graph.density(sg)
    density.list[i] = density.sg
    print(sprintf("Community %d has density = %.4f", i, density.sg))}
      
density.list[[27]]
```


Compute the ratio of inner clusters connections to outer ones:
```{r}
## Put your code here
for (i in seq(length(groups(mm)))){
    sg = induced_subgraph(g, mm$membership==i)
    ratio = ecount(sg)/(ecount(g)-ecount(sg))
    print(sprintf("Community %d has ratio = %.4f", i, ratio))}
```



### 3. Visualization & interpretation

Visulize five of the most dense clusters. Use names of artists as node labels on the graph.
```{r}
## Put your code here
artists = scan("artists.txt", character(), sep = "\n")
#artists
V(g)$label = artists
top5 = list()
for (i in seq(5)){
  
  i = which.max(density.list)
  top5=append(top5, density.list[i])
  density.list[i] = -1
  
  subgraph = induced.subgraph(g,which(mm$membership == i))
  plot(subgraph, layout=layout.circle)
  
}
```


```{r}
top5
```

<b> (Extra task) </b>Try to interpret (using Wikipedia or other resources) obtained clusters.

*Insert comments here*