---
title: "Social Network Analysis <br/> Home Assignment 2"
author: '{Your Name}'
date: "due date - 22.05.2017 23:59"
output:
  word_document:
    toc: yes
  pdf_document:
    toc: yes
  html_document:
    toc: yes
---
# Graph models. Centrality metrics
Please send your reports to hse.ntwks@gmail.com with the subject of of the following structure:<br/>
*[MAGOLEGO SNA 2017] {Mirzaaghayev} {Ramil} HA{2}*

Late submission policy: -1 point per day

Use this file as a template for your report.\
Support your computations with figures and comments. Send ONLY .Rmd versions of your report with datasets for your social network. Anonymize your data if necessary.

```{r, echo=FALSE}
library(igraph)
library(rgexf)
library(R.matlab)
```


## Task 1. Your social network

For the first task, you have to load your [vk.com](http://vk.com) network. Please follow the instructions posted on the course wiki or user [VK Application](vk.com/app3861133). For [FB](http://facebook.com) users try to use [NetVizz](http://thepoliticsofsystems.net/2010/03/netvizz-facebook-to-gephi/). If you did it correctly, you should have a GraphML file with your own network. Read it to R:

```{r}
## Put your code here
g = gexf.to.igraph(read.gexf("vk-friends-266010761.gexf"))

z = get.adjacency(g)
z.names = 1:vcount(g)
colnames(z) = z.names
rownames(z) = colnames(z)
g = graph.adjacency(z, add.colnames = TRUE)

V(g)$label.cex = 0.5

plot(g)
```

### 1. Degree distribution

First, plot degree distribution of your network in log-log scales:

```{r}
## Put your code here
p = degree.distribution(g, cumulative = FALSE)
pdf = p[which(p>0)]

plot(pdf, log="xy", main="PDF of the My VK Network", xlab="Degree", ylab="Frequency")
#KS test 
cdf = cumsum(pdf)
x = as.numeric(1:max(degree(g)))+1
g.fit = power.law.fit(x,implementation = "plfit")
x_min = g.fit$xmin
alpha = g.fit$alpha

func_CDF = function(x) return(1-(x_min^(alpha-1))*x^(1-alpha))
plot(cdf, log="xy", main="CDF of the My VK Network", xlab="Degree", ylab="Frequency")
par(new=TRUE)
curve(func_CDF, from=x_min, to = max(x), n=length(x),log="xy", col="red", add=FALSE, xlab = "", ylab = "", axes=FALSE)
legend("bottomright", c("alpha = ", alpha))

```

Is there any correspondence between actual degree distribution of your network and the Power Law distribution? If not, explain why.

There is not a good correspondance between the theoretical degree distribution and empirical data. This is due to the nature of empirical data. 

Now, let's see how it would look if it was random. Produce Erdos-Renyi graph matching your real network (same number of nodes and same average degree). Compare it with your degree distribution.

```{r}
## Put your code here
er = erdos.renyi.game(n=vcount(g), p.or.m = ecount(g), type=c("gnm"))
pdf.er = degree.distribution(er,cumulative = FALSE)
cdf.er = cumsum(pdf.er)

plot(pdf, log="xy", main="My VK Network vs Erdos Reyni Game", xlab="Degree", ylab="Frequency")
par(new=TRUE)
plot(pdf.er, log="xy",col="red",  xlab="", ylab="", add=FALSE, axes=FALSE)
legend("left", c("ER Game","VK Network"), col = c("red", "black"), lty=1)

```

*Put your comments here*

### 2. Compute centrality metrics

Compute for your network: 

* degree centrality

* closeness centrality

* betweenness centrality

* eigenvector centrality

* Bonacich power centrality

* Alpha centrality


```{r}
## Put your code here
# 1. degree centrality 
deg = degree(g)

# 2. closeness centrality
close = closeness(g)

# 3. betweenness centrality
btw = betweenness(g)

# 4.eigenvector centrality
eig = eigen_centrality(g)

# 5.Bonacich power centrality
bonc = bonpow(g)

# 6. Alpha centrality
alf = alpha.centrality(g)
```

Output six plots corresponding to six centrality metrics you've computed: 

* Use first names of your friends as node labels on the graph (you may hide this information if you wish -- change it by integer ID)
* Keep the same layout of the network
* Make node sizes and colours proportional to the respective centrality metrics

Hint: If you get stuck, lab 4 script might be helpful.

```{r}
## Put your code here

z = delete.vertices(g, degree(g)==0 )

scl = function(c) return(scale(c, center = min(c), scale = max(c) - min(c)))

color.palette = colorRampPalette(c('red','blue'))
colors = color.palette(50)[as.numeric(cut(deg, breaks = 50))]

plot(z, layout=layout.fruchterman.reingold(z), vertex.color=colors, vertex.size=scl(deg), main='Degree Centrality')


plot(z, layout=layout.fruchterman.reingold(z), vertex.color=colors, vertex.size=scl(close), main='Closeness Centrality')

plot(z, layout=layout.fruchterman.reingold(z), vertex.color=colors, vertex.size=scl(btw), main='Betweenness Centrality')

plot(z, layout=layout.fruchterman.reingold(z), vertex.color=colors, vertex.size=scl(alf), main='Alpha Centrality')

plot(z, layout=layout.fruchterman.reingold(z), vertex.color=colors, vertex.size=scl(eig$vector), main='Eigenvector Centrality')

plot(z, layout=layout.fruchterman.reingold(z), vertex.color=colors, vertex.size=scl(bonc), main='Bonacich Centrality')
```

Now, output top ten nodes in each ranking. Again, print only first names in your table to keep privacy:

```{r}
## Put your code here
top10 = function(c) return(which(c > sort(c)[ length(c)-10 ]))

data.frame(Rank=1:10, Degree_centrality=top10(deg))
data.frame(Rank=1:10, Closeness_centrality=top10(close))
data.frame(Rank=1:10, Bonacich_centrality=top10(bonc))
data.frame(Rank=1:10, Alpha_centrality=top10(alf))
data.frame(Rank=1:10, Betweenness_centrality=top10(btw))
data.frame(Rank=1:10, Eigenvector_centrality=top10(eig$vector))

```

*When I checked for 31st node it is my friend Nicko, he is my close friend and we communicate a lot and also he is a public figure. It is interesting seeing him both in degree centrality and eigenvector centrality in the top rank*


## Task 2. Flickr network

In the second task, you will work with a large directed graph. 

Please download [flickr.mat](http://www.hse.ru/data/2015/05/01/1098247366/flickr.mat) 

*Data contains sparse matrix A and list of user names. This is a denser part of the Flickr photo sharing site friendship graph from 2006. Edge direction corresponds to friendship requests (following). Some of the links are reciprocal, others not*

It's a Matlab file. How to deal with it in R? There is a package `R.matlab`. Please install it and call `library(R.matlab)`

Now use `readMat` function to read the file and extract adjacency matrix and a list of user names:

```{r}
flickr = readMat("flickr.mat")
fmatrix=as.matrix(flickr[1]$A)
fnames=flickr[2]$names

f = graph.adjacency(fmatrix)
```

If you have trouble loading large mat file on your laptop --- try to use HSE computer classes with installed R+RStudio.

Look at user names. You might want to remove spaces from the names. Use a function `gsub` to remove them:

```{r, eval=FALSE}
fnames=gsub(" ", "", fnames)
```

Now create a graph, output the number of vertices and edges:

```{r}
## Put your code here


paste("Number of vertices", vcount(f))
paste("Number of edges", ecount(f))
```

Compute in- and out- degree centralities, PageRank, Hubs and Authorities for this network:

```{r}
## Put your code here
f.deg.in = degree(f, mode="in")
f.deg.out = degree(f, mode="out")
f.pg.rnk = page.rank(f)
f.hubs = hub.score(f)
f.auth = authority.score(f)
```

Print top ten names in each ranking:

```{r}
## Put your code here
data.frame(Degree_in=top10(f.deg.in), Names = fnames[top10(f.deg.in)])
data.frame(DEgree_out=top10(f.deg.out), Names = fnames[top10(f.deg.out)])
data.frame(Page_rank=top10(f.pg.rnk$vector), Names = fnames[top10(f.pg.rnk$vector)])
data.frame(Hub_score=top10(f.hubs$vector), Names=fnames[top10(f.hubs$vector)])
data.frame(Authority_score=top10(f.auth$vector), Names=fnames[top10(f.auth$vector)])

```

Produce the following plots:

* In-degree centralities versus out-degree centralities

* In-degree centralities versus authorities

* Out-degree centralities versus hubs

* Hubs versus authorities

* PageRank versus hubs

* PageRank versus authorities


```{r}
## Put your code here
plot(f.deg.in, f.deg.out, xlab = "Degree in centrality", ylab = "Degree out centrality", col="Green", main="In-degree centralities versus out-degree centralities")

plot(f.deg.in, f.auth$vector, xlab = "Degree in centrality", ylab = "Authority", col="Blue", main="In-degree centralities versus authorities")

plot(f.deg.out, f.hubs$vector, xlab = "Degree out centrality", ylab = "Hubs", col="Grey", main="Out-degree centralities versus hubs")

plot(f.hubs$vector, f.auth$vector, xlab = "Hubs", ylab = "Authority", col="Red", main="Hubs versus authorities")

plot(f.pg.rnk$vector, f.auth$vector, xlab = "Page Rank", ylab = "Authority", col="Cyan", main="PageRank versus authorities")

plot(f.pg.rnk$vector, f.hubs$vector, xlab = "Page Rank", ylab = "Authority", col="Brown", main="PageRank versus hubs")

plot(f.deg.in, f.pg.rnk$vector)
```

*One can observe a strong correlation between,
1. Degree in centrality and Authority
2. Hubs and Degree out
3. Authority and Page rank
This also implies that Degree-in and Page rank also should be strongly correlated which was also plotted*
